The Wolf in Sheep's Clothing:\\ Subversive Adversarial Agent Identification

### 2016-08-11 article.tex
changed intro

\section{Introduction}
Robot security has landed headlines across a variety of commonly used networked devices, car hacking being a prominent example of a security flaw that could have catastrophic impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of Greenber et al, posing many questions about the protocol used in vehicles and how other cars in the same network can work to detect and isolate a compromised agent \cite{greenberg2015hackers}.

This network of agents is what is commonly referred to as a distributed system; a network of agents working to achieve a common goal. Among distributed systems come in a combination of centralized and decentralized characteristics, the two main extremes a system can be categorized as. Centralized systems have the advantage of control at the expense of one central point of failure, whereas a well structured decentralized system can be resilient to various attacks.

As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes are based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. In a full trust chain there is an initial block of trust called Hardware Secure Enclosure (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify various modules of an agent such as the static software, dynamic software, control system and communication between agents.

Communication between two agents focuses on confidentiality and integrity which can both be accounted for through proper encryption and the data fields inside the encrypted message. A challenge-response system is implemented in this paper which changes, or churns, on every round trip time providing fresh keys for the encrypted payload. The consequence of this design is that every communication is uniquely encrypted, closing doors for leakage of information. Timestamp and source mac address fields inside the encrypted payload ensures not only that the message comes from the individual claiming to be the originator in the raw packet, but also that timing attacks can be properly guarded against.

Once communication is secured, an adversary can distort the sensor data of an agent in order to lead it in a stray. An agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established \textit{usage envelope}, a pre-computed state trajectory map. This map allows for a large variety of planning algorithms to be used. In light that there is both sensor and mechanical error in the system a Bayes filter is used in order to implement proper weighing of new data coming in.

Redundant measurements in the system allow for an agents inside a trusted set to verify each other's locations. With and without feedback from others in the system, an agent is able to verify the positions of others relative to itself through the use of several Kalman filters.

We now relate some work related to integrity, availability, and confidentiality, and further discuss the implementation technique used. We then demonstrate our experiments and gather a conclusion from the results and motivation of the paper.

\section{Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as Adi et al where a DNA clone resistant approach is taken throughout~\cite{adi2009mechatronic}; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is the HSE which is used to verify other parts of the system much like Adi et al~\cite{adi2009mechatronic}.

\subsection{State Estimation}
State estimation is a fundamental problem for robotics. Without knowing its location, a robot cannot be very useful. One common technique for robot localization is to use a Kalman Filter (KF). The KF is one of the most studied and most heavily utilized Bayesian filter~\cite[39-81]{ProbabilisticRobotics}, and the application of the KF to the task of robot localization has been studied intently~\cite{Localization2003, Mohsin2014}. In \textcite{Mohsin2014}, it is explained to be so popular for three main reasons. First, it is optimal under certain reasonable and common assumptions, second that it is recursive which is memory efficient, and finally that it relies only on having knowledge of noisy sensor data and not being able to measure certain state variables directly~\cite{Mohsin2014}.

@@

\subsubsection{Confidentiality: Secure Ad-Hoc Channel Communication}
There are various works that cover a communications for adhoc networks. Vegh et al uses an extension of the ElGamal algorithm in order to limit the access of agents in the network\cite{vegh2014securing}. In the event that an agent is compromised the information within the decrypted message remains protected through steganography, a method used for hiding information within a text \cite{adi2009mechatronic}. The implementation uses direct agent to agent communication and thus no hierarchy is used; no encrypted broadcast messages are sent and it seems unnecessary to encrypt the information further as it would lead to potential DOS attacks.

@@

\section{Methodology}

@@

\section{Experiments}

@@

\section{Conclusion}
We have presented three components from a larger chain of trust that is designed to ensure security of not only the agent itself, but also of the group of agents surrounding it.

>>>>

\section{Introduction}
Robot security has landed headlines across a variety of commonly used networked devices, car hacking being a prominent example of a security flaw that could have catastrophic impact in the United States and abroad. Some individuals have been able to remotely connect to, disable, and control various vehicles in the market through techniques like that of \textcite{greenberg2015hackers}, posing many questions about the protocol used in vehicles and how other cars in the same network can work to detect and isolate a compromised agent. This network of agents come in a combination of centralized and distributed characteristics in order to achieve a common goal. Centralized systems have the advantage of control and lower cost at the expense of one central point of failure, whereas a well structured decentralized system can be resilient to various attacks due to its versatility. As more agents become connected, much like cyber-vehicles in a highway would, decisions that each agent makes can be based on the information it obtains from not only its sensors but also other agent's data. This paper discusses how an agent can securely obtain the probability that another agent in the system is compromised in order to trust feedback obtained from that agent in question.

There are three core goals for the security of any cyber-physical system: integrity, availability, and confidentiality \cite{Cardenas2008}. Those can be thought of as three simple questions: ``Can I trust the data?'', ``Do I have access to the data when I need it?'', and ``Is the data hidden from those who shouldn't have it?''. In a trust chain there is an initial block of trust called Hardware Security Engine (HSE) unit which fingerprints specific physical properties of the hardware to uniquely identify an agent. This fingerprint is used to verify various modules of an agent such as the static software, dynamic software, control system and communication between agents.

Communication between two agents focuses on confidentiality and integrity which can both be accounted for through proper encryption and meta-data inside the encrypted message. A challenge-response system is implemented in this paper which changes on every round trip time providing fresh keys for the uniquely encrypted payload. Timestamp and source mac address fields inside the encrypted payload not only ensure the identity of the sender, but also the timing integrity. Once communication is secured, an adversary can still distort the sensor data of an agent however. An agent in the group can detect the abnormality by comparing the state and behavior combination taken to that of an established \textit{usage envelope}, a pre-computed state trajectory map. This map allows for a large variety of planning algorithms to be used. The state of the agent is computed through the use of redundant measurements in the system which allow for an agents inside a trusted set to verify each other's locations.

The remainder of the paper will continue as follows. Related work pertaining to integrity, availability, and confidentiality will be presented in \ref{sec:Related Work}. The system design is introduced in section \ref{sec:Methodology} which further discusses the implementation techniques used. We then demonstrate our experiments in section \ref{Results} and the results obtained in section \ref{Results} and gather a conclusion from the results and motivation of the paper in section \ref{Conclusion}.

\section{Related Work} \label{sec:Related Work}
Chain of trusts, as pertaining to cyber systems, have been introduced in works such as that of~\textcite{adi2009mechatronic} where a DNA ideology was utilized to formulate a clone resistant agent; a Physical Unclonable Function (PUF) was introduced which obtains physical differences between other electronic devices. Similar to this work the extended chain of trust this paper is the HSE which is used to verify other parts of the system much like~\textcite{adi2009mechatronic}.

\subsection{State Estimation}
State estimation is a fundamental problem for robotics. Without knowing its location, a robot cannot be very useful. One common technique for robot localization is to use a Kalman Filter (KF). The KF is one of the most studied and most heavily utilized Bayesian filter~\cite[39-81]{ProbabilisticRobotics}, and the application of the KF to the task of robot localization has been studied intently~\cite{Localization2003, Mohsin2014}. In~\textcite{Mohsin2014}, it is explained to be so popular for three main reasons. First, it is optimal under certain reasonable and common assumptions, second that it is recursive which is memory efficient, and finally that it relies only on having knowledge of noisy sensor data and not being able to measure certain state variables directly~\cite{Mohsin2014}.

@@

\subsubsection{Confidentiality: Secure Ad-Hoc Channel Communication}
There are various works that cover a communications for adhoc networks. ~\textcite{vegh2014securing} uses an extension of the ElGamal algorithm in order to limit the access of agents in the network. In the event that an agent is compromised the information within the decrypted message remains protected through steganography, a method used for hiding information within a text \cite{adi2009mechatronic}. The implementation uses direct agent to agent communication and thus no hierarchy is used; no encrypted broadcast messages are sent and it seems unnecessary to encrypt the information further as it would lead to potential DOS attacks.

@@

\section{Methodology} \label{sec:Methodology}

@@

\section{Experiments} \label{Experiments}

@@

\section{Results} \label{Results}

\section{Conclusion} \label{Conclusion}
We have presented three components from a larger chain of trust that is designed to ensure security of not only the agent itself, but also of the group of agents surrounding it.
